\documentclass{article}

\input{preamble}
\input{definitions}

\begin{document}

\noindent
Dear managing editor at Nano Letters,
\bigbreak
We are writing to inquire about the suitability of our manuscript
"A Bayesian Solution to Count the Number of Molecules within a Diffraction Limited Spot" 
for publication in Nano Letters. 
%
Broadly, we believe this manuscript would be of great interest to you and your readers
as it proposes a new method for quantifying biological phenomena at the nano-scale.
%
This manuscript proposes a significant new method in the fields of super-resolution
and single molecule fluorescent imaging, and would be a good fit for nano Letters, 
given your journals history of publishing on related work. 
%
% We have noticed that your journal has a significant history of publishing on
% super-resolution and single-molecule fluorescence microscopy, and this manuscript 
% proposes a significant new method building on this body of work. 


Specifically, in this manuscript we propose a new method of quantifying the 
number of fluorescent emitters within a diffraction limited spot, 
a common problem when imaging biology at the nano-scale.
%
We solve this by directly modeling the photophysics and kinetics over time 
to produce a probabilistic estimate of the number of emitters. 
%
We demonstrate a 2-fold increase in accuracy compared to the current 
state of the art methods, and show that our method is applicable to a 
wider range of experimental systems, increasing its accessibility. 
%

Please see our pre-print on BioRxiv for more information, and let 
us know if you have any questions regarding the manuscript. 

\bigbreak
\noindent
https://www.biorxiv.org/content/10.1101/2024.04.18.590066v2.abstract

\bigbreak
\noindent
Thank you very much, and we look forward to hearing from you.

\bigbreak
\noindent
Alex Hillsley and Jan Funke

\noindent
HHMI Janelia Research Campus



\end{document}
